Implications of afforestation policies for global markets

### 2024-02-25 paper.Rmd
Update paper.Rmd

[@defries2010] found a strong correlation between forest loss and exports of agricultural products. On the other hand, [@turner2005] investigated the role of trade on forests in the context of the Free Trade Area of the Americas (FTAA) using the spatial partial-equilibrium Global Forest Products Model and found that FTAA has a positive impact on forest resources.

# References

>>>>

These reductions in the amount of agricultural land prompt changes in the quantity of agricultural goods produced for many regions. For example, East Asia and Southeast Asia see the largest declines in percentage terms in agricultural production with decreases of 5.9 percent and 2.8 percent, respectively (Table 2). Surprisingly, Brazil and the United States, despite the derease in available agricultural land compared to the baseline 2030 scenario, see increased agricultural output of 0.2 percent and 0.8 percent, respectively. This may be tied to the sharp declines in other regions prompting greater production for export.

Table 2
			∆ (%)
East Asia		-5.9
Southeast Asia		-2.8
Central America		-2.7
South Asia		-2.1
Rest of South America	-1.6
North Africa & the Middle East	-1.2
Sub-Saharan Africa	-0.5
China			-0.1
Russia			0.1
Brazil			0.2
EUII			0.3
European Union		0.4
United States		0.8
Oceania			0.9
Canada			1.3
Japan			1.5

When we examine how this impacts exports of agricultural goods, we find that Japan and the United States appear to be the biggest beneficiaries of this policy with their exports increasing 13.5 percent and 5.0 percent, respectively (table 3). The regions where agricultural exports drop most significantly are South Asia, Southeast Asia, and Central America who see decreases of 11.0 percent, 7.3 percent, and 6.9 percent, respectively.

Table 3
				∆ (%)
				Agriculture
Japan				13.5
United States			5.0
Canada				2.6
Russia				2.4
Oceania				2.2
EUII				2.2
China				1.5
European Union			1.4
Brazil				1.4
Sub-Saharan Africa		0.0
North Africa & the Middle East	-2.3
Rest of South America		-3.8
Central America			-6.9
Southeast Asia			-7.3
South Asia			-11.0
East Asia			-19.8

Overall, this policy, while avoiding deforestation, has a rather significant negative economic impact on all regions except Japan and Canada who see an increase in consumer well-being of $977.1 million and $166.9 million, respectively (table 4). Consumer well-being is a measurement of equivalent variation and here measures the benefit/harm consumers experience in terms of income as a result of the policy changes. The United States, along with 10 other regions, see well-being drop by more than $1 billion. The most negatively impacted regions are South Asia (-28.0 billion), China (-14.5 billion), and Southeast Asia (-13.6 billion). In total, such a policy is estimated to decrease global consumer well-being by $92.1 billion.

Table 4
				∆ ($)
Japan				977,125,000
Canada				166,937,500
Oceania				-169,625,000
EUII				-588,500,000
Brazil				-735,125,000
United States			-1,085,000,000
Russia				-1,152,375,000
Rest of South America		-3,848,625,000
Central America			-4,471,500,000
North Africa & the Middle East	-5,012,125,000
East Asia			-5,065,625,000
European Union			-7,152,500,000
Sub-Saharan Africa		-7,850,500,000
Southeast Asia			-13,601,000,000
China				-14,452,000,000
South Asia			-28,024,000,000

[@defries2010] found a strong correlation between forest loss and exports of agricultural products. On the other hand, [@turner2005] investigated the role of trade on forests in the context of the Free Trade Area of the Americas (FTAA) using the spatial partial-equilibrium Global Forest Products Model and found that FTAA has a positive impact on forest resources.
# References
